---
title: "Leaflet_practice"
output: html_document
---

```{r}
library(leaflet)
```

Look at the city of Lexington
```{r}
leaflet() %>% setView(lng = -79.442778, lat = 37.783889, zoom = 12) %>% addTiles()
```
Looks at the world at night
```{r}
leaflet() %>% 
  setView(lng = -79.442778, lat = 37.783889, zoom = 8) %>% 
  addProviderTiles(provider = providers$NASAGIBS.ViirsEarthAtNight2012)
```

Provides a light map to emphasize things on the map
```{r}
leaflet() %>% 
  setView(lng = -79.442778, lat = 37.783889, zoom = 12) %>% 
  addProviderTiles(providers$CartoDB.Positron)
```

Shows the real time data of the weather in an area
```{r}
leaflet() %>% 
  addTiles() %>% 
  setView(lng = -79.442778, lat = 37.783889, zoom = 8) %>%
  addWMSTiles(
    "http://mesonet.agron.iastate.edu/cgi-bin/wms/nexrad/n0r.cgi",
    layers = "nexrad-n0r-900913",
    options = WMSTileOptions(format = "image/png", transparent = TRUE),
    attribution = "Weather data © 2012 IEM Nexrad"
  )
```

Data that will be imposed on the map of lexington: 
```{r}
lex <- data.frame( lat    = c(37.789444 , 37.787673  ,  37.785624  )
                 , lon    = c(-79.441725, -79.443623 , -79.441544  )
                 , place  = c("Lab"     , "Classroom", "Thai food!")
                 , rating = c(7         , 5          , 10          )
                 , stringsAsFactors = FALSE
                 )
```

Make markers on the map where there is data points: 
```{r}
leaflet(data = lex) %>% 
  addTiles() %>% 
  addMarkers(popup = ~place)
```


Add a marker to show the number of markers in an area:
```{r}
leaflet(data = lex) %>% 
  setView(lng = -79.442778, lat = 37.783889, zoom = 10) %>% 
  addTiles() %>% 
  addMarkers(label = ~place, clusterOptions = markerClusterOptions())
```

Can add different kinds of circles with varying radius' based on quantitative data: 
*Note: 
In addCircleMarkers it specifies the size in pixels (image-land); no matter the zoom the circles are always the same size
In addCircles it specifies the size in meters (real-world); so they get bigger or smaller when you zoom.
```{r}
leaflet(data = lex) %>% addTiles() %>%
  addCircles(radius = ~rating, label = ~place)
```












